---
title: "R Notebook"
output: html_notebook
---

#Libraries
```{r}
#Dimension de las imagenes: w: 879 y h: 305
#Dimension de las imagenes en fila: w:340 y h:320
suppressMessages(library(tidyverse))
suppressMessages(library(ggplot2))
suppressMessages(library(dplyr))
```

#Learning Rate Analisys (Simple RF)
```{r}
feature_vectors_cleaned <- read.csv('./datasets/balanced_feature_vector_cleaned.txt', stringsAsFactors = F, sep = '|')

rf_data <- read.csv('./datasets/random_forest_30_iterations_f1_testing2.txt',sep = '|', stringsAsFactors = F)
rf_data <- rf_data %>% filter(count_of_data < 9000)
data_means <- rowMeans(rf_data[,c(-1)])
#data_means
result_data_2 <- rf_data[,-1]
data_sd <- transform(result_data_2, SD=apply(result_data_2,1, sd, na.rm = TRUE))
#data_sd[,'SD']

size_features_vector <- nrow(feature_vectors_cleaned)
step_size <- 200
split_size_training = size_features_vector / step_size
values<-c()
#vector_sampled
for (i in 1:44){
    values[i] = i*step_size
}
values
aux_data <- cbind(ds=data_sd[,'SD'],m=data_means)
aux_data
data<-as.data.frame(cbind(x=values,cluster=aux_data))
data[,'m'] - (data[,'ds'] / 2)
names(data) <- c("x","ds","m")
data
pd <- position_dodge(0.5)
learning_rate_plot <- ggplot(data, aes(x=x,y=m))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line(color='red') + 
  geom_point(color = 'red') +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "training-set size",
       y="F1 Score", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))

learning_rate_plot
```


#Learning Rate Analisys (Uncertaining Sampled result)
```{r}
rf_data_uncertain <- read.csv('./datasets/balanced_random_forest_30_iterations_f1_testing_uncertaining_sampled.txt',sep = '|', stringsAsFactors = F)
rf_data_uncertain <- rf_data_uncertain %>% filter(count_of_data < 9000)
#data_means <- rowMeans(rf_data_uncertain[,c(-1)])
#data_means
#result_data_2 <- rf_data_uncertain[,-1]
data_sd_uncertaining <- transform(rf_data_uncertain[,-1], SD=apply(rf_data_uncertain[,-1],1, sd, na.rm = TRUE))
#data_sd[,'SD']

#aux_data <- cbind(ds=data_sd_uncertaining[,'SD'],m=rowMeans(rf_data_uncertain[,c(-1)]))
#aux_data
data_uncertain <- as.data.frame(cbind(x=values, cluster = cbind(ds=data_sd_uncertaining[,'SD'], m = rowMeans(rf_data_uncertain[,c(-1)]))))
data_uncertain[,'m'] - (data_uncertain[,'ds'] / 2)
names(data_uncertain) <- c("x","ds","m")

pd <- position_dodge(0.5)
learning_rate_plot_uncertain <- ggplot(data_uncertain, aes(x=x,y=m))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line(color='red') + 
  geom_point(color = 'red') +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "training-set size",
       y="F1 Score", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))

learning_rate_plot_uncertain
```

#Logistic Regresion Analisys (Uncertaining Sampled result)
```{r}
lr_data_uncertain <- read.csv('./datasets/balanced_logistic_regression_30_iterations_f1_testing.txt',sep = '|', stringsAsFactors = F)
lr_data_uncertain <- lr_data_uncertain %>% filter(count_of_data < 9000)
#data_means <- rowMeans(rf_data_uncertain[,c(-1)])
#data_means
#result_data_2 <- rf_data_uncertain[,-1]
data_sd_uncertaining <- transform(lr_data_uncertain[,-1], SD=apply(lr_data_uncertain[,-1],1, sd, na.rm = TRUE))
#data_sd[,'SD']

#aux_data <- cbind(ds=data_sd_uncertaining[,'SD'],m=rowMeans(rf_data_uncertain[,c(-1)]))
#aux_data
data_uncertain_lr <- as.data.frame(cbind(x=values, cluster = cbind(ds=data_sd_uncertaining[,'SD'], m = rowMeans(lr_data_uncertain[,c(-1)]))))
data_uncertain_lr[,'m'] - (data_uncertain_lr[,'ds'] / 2)
names(data_uncertain_lr) <- c("x","ds","m")

pd <- position_dodge(0.5)
learning_rate_plot_uncertain <- ggplot(data_uncertain_lr, aes(x=x,y=m))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line(color='red') + 
  geom_point(color = 'red') +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "training-set size",
       y="F1 Score", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))

learning_rate_plot_uncertain
```

#Logistic Regresion Analisys (Random selection result)
```{r}
lr_data <- read.csv('./datasets/logistic_regression_30_iterations_f1_testing.txt',sep = '|', stringsAsFactors = F)
lr_data <- lr_data %>% filter(count_of_data < 9000)
#data_means <- rowMeans(rf_data_uncertain[,c(-1)])
#data_means
#result_data_2 <- rf_data_uncertain[,-1]
data_sd <- transform(lr_data[,-1], SD=apply(lr_data[,-1],1, sd, na.rm = TRUE))
#data_sd[,'SD']

#aux_data <- cbind(ds=data_sd_uncertaining[,'SD'],m=rowMeans(rf_data_uncertain[,c(-1)]))
#aux_data
data_lr <- as.data.frame(cbind(x=values, cluster = cbind(ds=data_sd[,'SD'], m = rowMeans(lr_data[,c(-1)]))))
data_lr[,'m'] - (data_lr[,'ds'] / 2)
names(data_lr) <- c("x","ds","m")

pd <- position_dodge(0.5)
learning_rate_plot_uncertain <- ggplot(data_lr, aes(x=x,y=m))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line(color='red') + 
  geom_point(color = 'red') +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "training-set size",
       y="F1 Score", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))

learning_rate_plot_uncertain
```
```{r}
partial_data_1 <- read.csv('./datasets/ilab_10_iterations_f1_testing_1.txt', sep = '|', stringsAsFactors = F)
partial_data_2 <- read.csv('./datasets/ilab_10_iterations_f1_testing_2.txt', sep = '|', stringsAsFactors = F)
partial_data_3 <- read.csv('./datasets/ilab_10_iterations_f1_testing_3.txt', sep = '|', stringsAsFactors = F)
vector_names <- c('count_of_data', 'iteration_15', 'iteration_16', 'iteration_17', 'iteration_41', 'iteration_51', 'iteration_61', 'iteration_71', 'iteration_81', 'iteration_91', 'iteration_101')

names(partial_data_3) <- vector_names
partial_data_aux <- cbind(partial_data_1,partial_data_2[,-1])

partial_data_aux <- cbind(partial_data_aux,partial_data_3[,-1])

x <- c('count_of_data')
for(i in c(1:30)){
  x[i+1] <- paste('iteration_',toString(i),sep = "")
}
x
names(partial_data_aux) <- x
partial_data_aux
```

#ILAB
```{r}
ilab_data <- partial_data_aux#read.csv('./datasets/balanced_ilab_30_iterations_f1_testing.txt',sep = '|', stringsAsFactors = F)
ilab_data <- ilab_data %>% filter(count_of_data < 9000)
#data_means <- rowMeans(rf_data_uncertain[,c(-1)])
#data_means
#result_data_2 <- rf_data_uncertain[,-1]
ilab_data_sd <- transform(ilab_data[,-1], SD=apply(ilab_data[,-1],1, sd, na.rm = TRUE))
#data_sd[,'SD']

#aux_data <- cbind(ds=data_sd_uncertaining[,'SD'],m=rowMeans(rf_data_uncertain[,c(-1)]))
#aux_data
ilab_data_lr <- as.data.frame(cbind(x=values, cluster = cbind(ds=ilab_data_sd[,'SD'], m = rowMeans(ilab_data[,c(-1)]))))
ilab_data_lr[,'m'] - (ilab_data_lr[,'ds'] / 2)
names(ilab_data_lr) <- c("x","ds","m")

pd <- position_dodge(0.5)
ilab_plot <- ggplot(ilab_data_lr, aes(x=x,y=m))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line(color='red') + 
  geom_point(color = 'red') +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "training-set size",
       y="F1 Score", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))

ilab_plot
```

#ILAB using RF
```{r}
ilab_rf_data <- read.csv('./datasets/balanced_rf_ilab_30_iterations_f1_testing.txt',sep = '|', stringsAsFactors = F)
ilab_rf_data <- ilab_rf_data %>% filter(count_of_data < 9000)
ilab_rf_data_sd <- transform(ilab_rf_data[,-1], SD=apply(ilab_rf_data[,-1],1, sd, na.rm = TRUE))

values<-c()
step_size <- 200
for (i in 1:44){
    values[i] = i*step_size
}

ilab_rf_data_lr <- as.data.frame(cbind(x=values, cluster = cbind(ds=ilab_rf_data_sd[,'SD'], m = rowMeans(ilab_rf_data[,c(-1)]))))
ilab_rf_data_lr[,'m'] - (ilab_rf_data_lr[,'ds'] / 2)
names(ilab_rf_data_lr) <- c("x","ds","m")

pd <- position_dodge(0.5)
ilab_rf_plot <- ggplot(ilab_rf_data_lr, aes(x=x,y=m))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line(color='red') + 
  geom_point(color = 'red') +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "training-set size",
       y="F1 Score", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))

ilab_rf_plot
```


#################### Robustness Analysis ###############################
#Robusness Analysis in RF using new balanced dataset 
```{r}
#noisy_rf_accuracy <- read.csv('./datasets/balanced_test_result_rf_accuracy.txt', stringsAsFactors = F, sep = '|')
noisy_rf_ela_1 <- read.csv('/home/jguerra/datasets/stratosphere/balanced_test_result_ela_measure.txt', stringsAsFactors = F, sep = '|')
noisy_rf_ela_2 <- read.csv('/home/jguerra/datasets/stratosphere/balanced_test_result_ela_measure_2.txt', stringsAsFactors = F, sep = '|')
noisy_rf_ela_3 <- read.csv('/home/jguerra/datasets/stratosphere/balanced_test_result_ela_measure_3.txt', stringsAsFactors = F, sep = '|')

merge_data <- cbind(noisy_rf_ela_1, noisy_rf_ela_2[,-1])
merge_data <- cbind(merge_data, noisy_rf_ela_3[,-1])
ncol(merge_data)
merge_data <- merge_data[,-2]

name = c(c('porcent_of_data') ,paste('it',c(1:30), sep = '_'))
#names(noisy_rf_accuracy) <- name
names(merge_data) <- name

#noisy_rf_accuracy
noisy_rf_ela <- merge_data
```

#Plotting Robusness Analysis in RF using CTU-19
```{r}
data_means <- rowMeans(noisy_rf_ela[,c(-1)])
#data_means
cs_pred_2 <- noisy_rf_ela[,-1]
data_sd <- transform(cs_pred_2, SD=apply(cs_pred_2,1, sd, na.rm = TRUE))
#data_sd[,'SD']

aux_data <- cbind(ds=data_sd[,'SD'],m=data_means)
#aux_data
data_rf_ctu19<-as.data.frame(cbind(x=noisy_rf_ela[,1],cluster=aux_data))
data_rf_ctu19[,'m'] - (data_rf_ctu19[,'ds'] / 2)
names(data_rf_ctu19) <- c("x","ds","m")
#data
pd <- position_dodge(0.5)
robustness_plot <- ggplot(data_rf_ctu19, aes(x=x,y=m))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line(color='red') + 
  geom_point(color = 'red') +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "Noise Level [%]",
       y="ELA Measure", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))
robustness_plot
```

#Robusness Analysis in ILAB new balanced dataset 
```{r}
noisy_ilab_accuracy <- read.csv('/home/jguerra/datasets/stratosphere/balanced_ilab_test_result_rf_accuracy.txt', stringsAsFactors = F, sep = '|')
noisy_ilab_ela <- read.csv('/home/jguerra/datasets/stratosphere/balanced_ilab_test_result_ela_measure.txt', stringsAsFactors = F, sep = '|')

name = c(c('porcent_of_data') ,paste('it',c(1:30), sep = '_'))
names(noisy_ilab_accuracy) <- name
names(noisy_ilab_ela) <- name

#noisy_ilab_accuracy
#noisy_ilab_ela
```

#Plotting Robusness Analysis in ILAB
```{r}
data_means <- rowMeans(noisy_ilab_ela[,c(-1)])
#data_means
cs_pred_2 <- noisy_ilab_ela[,-1]
data_sd <- transform(cs_pred_2, SD=apply(cs_pred_2,1, sd, na.rm = TRUE))
#data_sd[,'SD']

aux_data <- cbind(ds=data_sd[,'SD'],m=data_means)
#aux_data
data_ilab_ctu19<-as.data.frame(cbind(x=noisy_ilab_ela[,1],cluster=aux_data))
data_ilab_ctu19[,'m'] - (data_ilab_ctu19[,'ds'] / 2)
names(data_ilab_ctu19) <- c("x","ds","m")
#data
pd <- position_dodge(0.5)
robustness_plot <- ggplot(data_ilab_ctu19, aes(x=x,y=m))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line(color='red') + 
  geom_point(color = 'red') +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "Noise Level [%]",
       y="ELA Measure", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))
robustness_plot
```

#Combining Graph
```{r}
plot_result <- combining_graph(data_rf_ctu19,data_ilab_ctu19, text_group1 = 'RF', text_group2 = 'ILAB', caption = 'CTU-19', x_text = 'Noise Level [%]', y_text = 'ELA Measure')
plot_result
```

#Robusness Analysis in ILAB CTU-13 dataset
```{r}
noisy_ilab_accuracy <- read.csv('/home/jguerra/datasets/stratosphere/ctu13_ilab_test_result_rf_accuracy.txt', stringsAsFactors = F, sep = '|')
noisy_ilab_ela <- read.csv('/home/jguerra/datasets/stratosphere/ctu13_ilab_test_result_ela_measure.txt', stringsAsFactors = F, sep = '|')

name = c(c('porcent_of_data') ,paste('it',c(1:30), sep = '_'))
names(noisy_ilab_accuracy) <- name
names(noisy_ilab_ela) <- name

head(noisy_ilab_accuracy)
head(noisy_ilab_ela)
```

#Plotting Robusness Analysis in ILAB
```{r}
data_means <- rowMeans(noisy_ilab_ela[,c(-1)])
#data_means
cs_pred_2 <- noisy_ilab_ela[,-1]
data_sd <- transform(cs_pred_2, SD=apply(cs_pred_2,1, sd, na.rm = TRUE))
#data_sd[,'SD']

aux_data <- cbind(ds=data_sd[,'SD'],m=data_means)
#aux_data
data<-as.data.frame(cbind(x=noisy_ilab_ela[,1],cluster=aux_data))
data[,'m'] - (data[,'ds'] / 2)
names(data) <- c("x","ds","m")
#data
pd <- position_dodge(0.5)
robustness_plot <- ggplot(data, aes(x=x,y=m))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line(color='red') + 
  geom_point(color = 'red') +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "Noise Level [%]",
       y="ELA Measure", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))
robustness_plot
```

#Useful Function
```{r}
build_data <- function(dir){
  data <- read.csv(dir,sep = '|', stringsAsFactors = F) %>% filter(count_of_data < 9000)
  data_sd <- transform(data[,-1], SD=apply(data[,-1],1, sd, na.rm = TRUE))
  data <- as.data.frame(cbind(x=values, cluster = cbind(ds=data_sd[,'SD'], m = rowMeans(data[,c(-1)]))))
  data[,'m'] - (data[,'ds'] / 2)
  names(data) <- c("x","ds","m")
  return(data)
}

combining_graph <- function(data1,data2, text_group1, text_group2,  caption, x_text, y_text){
  visual1 <- data1
  visual2 <- data2
  
  visual1$group <- text_group1
  visual2$group <- text_group2
  visual1$group <- as.factor(visual1$group)
  visual2$group <- as.factor(visual2$group)
  
  visual12 <- rbind(visual1, visual2)
  visual12$group <- as.factor(visual12$group)
  
  plot_result <- ggplot(visual12, aes(x=x,y=m,  group=group, col=group, fill=group))+
    #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
    geom_line() + 
    geom_point() +
    geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
    #geom_boxplot()+
    labs(
         #title="Random Forest performance with incremental training data", 
         #subtitle="Drawn from Long Data format", 
         caption=caption, 
         x = x_text,
         y = y_text, 
         color=NULL) +
    theme_bw() +
    theme(axis.text = element_text(size = 12),
          axis.title = element_text(size = 14))
  return(plot_result)
}
```

### Combining graphs of Learning Rate result in Random Forest and Learning Rate result in Uncertaining Sampled
```{r}
visual1 <- data
#c_2 <- nrow(data_uncertain)
visual2 <- data_uncertain  #[-c(c_2, c_2 - 1, c_2 - 2, c_2 - 3, c_2 - 4, c_2 - 5),]
visual3 <- data_uncertain_lr
visual4 <- data_lr
visual5 <- ilab_data_lr
visual6 <- ilab_rf_data_lr

visual1$group <- 'RF using Random selection'
visual2$group <- 'RF using Uncertaining seleccion'
visual3$group <- 'LR using Uncertaining seleccion'
visual4$group <- 'LR using Random selection'
visual5$group <- 'ILAB'
visual6$group <- 'ILAB using RF'

visual1$group <- as.factor(visual1$group)
visual2$group <- as.factor(visual2$group)
visual3$group <- as.factor(visual3$group)
visual4$group <- as.factor(visual4$group)
visual5$group <- as.factor(visual5$group)
visual6$group <- as.factor(visual6$group)


visual12 <- rbind(visual1, visual2)
visual123 <- rbind(visual12, visual3)
visual1234 <- rbind(visual123, visual4)
visual12345 <- rbind(visual1234, visual5)
visual12345$group <- as.factor(visual12345$group)



visual_aux12 <- rbind(visual1, visual2)
visual_aux125 <- rbind(visual_aux12, visual5)
visual_aux125$group <- as.factor(visual_aux125$group)

#do.call(rbind, Map(data.frame, data_count=count_random, metric=metric)) %>%

ggplot(rbind(visual2, visual6), aes(x=x,y=m,  group=group, col=group, fill=group))+
  #geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  geom_line() + 
  geom_point() +
  geom_errorbar(aes(ymin=m-(ds/2), ymax=m+(ds/2)), colour="black", width=0.2) +
  #geom_boxplot()+
  labs(
       #title="Random Forest performance with incremental training data", 
       #subtitle="Drawn from Long Data format", 
       caption="Source: CTU-13", 
       x = "training-set size",
       y="F1 Score", 
       color=NULL) +
  theme_bw() +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 14))

```

```{r}
ilab_data$type= 'ilab'

rf_data_uncertain$type = 'RF'



rbind(ilab_data, rf_data_uncertain) %>% 
  reshape2::melt(id = c('count_of_data','type')) %>%
  ggplot()+
  geom_boxplot(aes(x = as.factor(count_of_data), y = value)) + 
  geom_point(aes(x = as.factor(count_of_data), y = value), color= 'red', alpha=0.2) + 
  facet_wrap(~type)
#ggplot(ilab_data,)
```